Simulation Modeling of Glycosylation Effects on Potassium Channels of Mouse Cardiomyocytes

### 2021-06-22 draft_plos.tex
Figure titles

\begin{figure}[!ht]
    \centering
    \caption{Simulation results of the (a) action potential and (b) relevant ionic currents (i.e., I\textsubscript{Kto}, I\textsubscript{Kslow}, I\textsubscript{Kss}, I\textsubscript{Na}, and I\textsubscript{CaL}) of mouse ventricular myocytes. Potassium currents have positive currents, while sodium and calcium currents are negative.}
    \label{fig1}
\end{figure}

\begin{figure}[!ht]
    \centering
    \caption{Predominant ion channels in human ventricular myocytes and their functional role in shaping an AP.}
    \label{fig2}
\end{figure}

@@

@@

\begin{figure}[!ht]
    \centering
    \caption{Example of K\textsuperscript{+} current decomposition into three component currents. Each component K\textsuperscript{+} current has different characteristics in terms of their peak and decaying phase.}
    \label{fig3}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{In-vitro experimental results, adopted from \cite{ednie2019reduced}, of averages and error bars of (a) the peaks and constant current, and (b) inactivation time constant. As reported in \cite{ednie2019reduced}, significant differences between WT and Mgat1KO at $p \leq 0.05$ are indicated by an *. ($n=35$ for WT and $n=38$ for Mgat1KO).}
    \label{fig4}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{An illustration of proposed self-breeding genetic algorithm and comparison with standard genetic algorithm.}
    \label{fig5}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{The comparison of current traces between calibrated simulations models (gray line) and benchmark exponential fitting (blue lines: WT; red lines: Mgat1KO). Each plot includes 30 replications of simulations results.}
    \label{fig6}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{Predicted current traces of I\textsubscript{Kto} and I\textsubscript{Kslow} for each group. (a) Current traces of WT and (b) for Mgat1KO. Clamp voltages of 4.5 seconds were applied to from -60 mV to +50 mV by 10-mV increments from the holding potential -70 mV.}
    \label{fig7}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{Predicted current density to voltage relationship for I\textsubscript{Kto} and I\textsubscript{Kslow} under Mgat1KO (red solid line with circle markers) and WT conditions (blue dotted line with square markers). Amplitudes were recorded for voltage steps ranging from -60 mV to 50 mV by 10-mV increments.} 
    \label{fig8}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{The prediction of inactivation time constants for I\textsubscript{Kto} and I\textsubscript{Kslow} with voltage steps from -60 mV to 50 mV by 10 mV steps.} 
    \label{fig9}
\end{figure}

\begin{figure}[!ht]
    \centering
    \caption{The prediction of SSI for I\textsubscript{Kto} and I\textsubscript{Kslow} with voltage steps from -60 mV to 50 mV by 10 mV steps.} 
    \label{fig10}
\end{figure}

>>>>

\begin{figure}[!ht]
    \centering
    \caption{{\bf Simulation model of mouse myocytes.} 
    Simulation results of the (a) action potential and (b) relevant ionic currents (i.e., I\textsubscript{Kto}, I\textsubscript{Kslow}, I\textsubscript{Kss}, I\textsubscript{Na}, and I\textsubscript{CaL}) of mouse ventricular myocytes. Potassium currents have positive currents, while sodium and calcium currents are negative.}
    \label{fig1}
\end{figure}

\begin{figure}[!ht]
    \centering
    \caption{{\bf Human ventricular action potential.} 
    Predominant ion channels in human ventricular myocytes and their functional role in shaping an AP.}
    \label{fig2}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{{\bf Dominant K\textsuperscript{+} cureents.} 
    Example of K\textsuperscript{+} current decomposition into three component currents. Each component K\textsuperscript{+} current has different characteristics in terms of their peak and decaying phase.}
    \label{fig3}
\end{figure}

@@

@@

\begin{figure}[!ht]
    \centering
    \caption{{\bf In-vitro experimental results.} 
    In-vitro experimental results, adopted from \cite{ednie2019reduced}, of averages and error bars of (a) the peaks and constant current, and (b) inactivation time constant. As reported in \cite{ednie2019reduced}, significant differences between WT and Mgat1KO at $p \leq 0.05$ are indicated by an *. ($n=35$ for WT and $n=38$ for Mgat1KO).}
    \label{fig4}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{{\bf Method illustration.} 
    An illustration of proposed self-breeding genetic algorithm and comparison with standard genetic algorithm.}
    \label{fig5}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{{\bf Comparison of simulation modeling and exponential fitting.} 
    The comparison of current traces between calibrated simulations models (gray line) and benchmark exponential fitting (blue lines: WT; red lines: Mgat1KO). Each plot includes 30 replications of simulations results.}
    \label{fig6}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{{\bf Prediction of current traces.} 
    Predicted current traces of I\textsubscript{Kto} and I\textsubscript{Kslow} for each group. (a) Current traces of WT and (b) for Mgat1KO. Clamp voltages of 4.5 seconds were applied to from -60 mV to +50 mV by 10-mV increments from the holding potential -70 mV.}
    \label{fig7}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{{\bf Prediction of density to voltage relationship.} 
    Predicted current density to voltage relationship for I\textsubscript{Kto} and I\textsubscript{Kslow} under Mgat1KO (red solid line with circle markers) and WT conditions (blue dotted line with square markers). Amplitudes were recorded for voltage steps ranging from -60 mV to 50 mV by 10-mV increments.} 
    \label{fig8}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \caption{{\bf Prediction of inactivation time constant.} 
    The prediction of inactivation time constants for I\textsubscript{Kto} and I\textsubscript{Kslow} with voltage steps from -60 mV to 50 mV by 10 mV steps.} 
    \label{fig9}
\end{figure}

\begin{figure}[!ht]
    \centering
    \caption{{\bf Prediction of SSI.} The prediction of SSI for I\textsubscript{Kto} and I\textsubscript{Kslow} with voltage steps from -60 mV to 50 mV by 10 mV steps.} 
    \label{fig10}
\end{figure}
